### 2020-04-29 final_report/results.tex
add multislice (exp2) description

We begin by evaluating a diverse set of surrogate families that we proposed
earlier. In particular, we aim to study considered models in terms of regression
performance and prediction time.
Following~\cref{sec:experiment-methodology}, where we proposed four experiments
that accomplish this task, we present and discuss our results in the next
sections.

@@

The first two experiments perform Bayesian optimisation to maximise~$R^2$ in
a cross-validation setting as a function of model hyperparameters. While in the
first experiment we limit training and testing sets to the scope of four slices of the
feature space, in the second experiment we lift this restriction.

@@

% TODO: do the same thing for the second experiment
\newpage
\begin{wrapfigure}{r}{0.333\textwidth}
	\centering
	\vspace{-3ex}
	\includegraphics[width=\linewidth]{exp2_time_vs_reg}
	\caption{Results of experiment~2, plotted analogously
	to~\cref{fig:exp1-time-vs-reg}.}
	\label{fig:exp2-time-vs-reg}
	\vspace{-4ex}
\end{wrapfigure}

% TODO: multislice description
TODO: multislice description

>>>>

We begin by comparing a diverse set of surrogate families that we proposed
to evaluate on previously collected samples of the expensive MC TBR model.
Through the four experimental cases described
in~\cref{sec:experiment-methodology}, we aim to study properties of the
considered models in terms of regression performance, training and prediction
time. In the next sections, we present and discuss our results.

@@

The first two experiments perform Bayesian optimisation to maximise~$R^2$ in
a cross-validation setting as a function of model hyperparameters. While in the
first experiment we limit training and test sets to the scope of four selected
slices of the feature space, in the second experiment we lift this restriction.

@@

\begin{wrapfigure}{r}{0.333\textwidth}
	\centering
	\vspace{-3ex}
	\includegraphics[width=\linewidth]{exp2_time_vs_reg}
	\caption{Results of experiment~2, plotted analogously
	to~\cref{fig:exp1-time-vs-reg}.}
	\label{fig:exp2-time-vs-reg}
	\vspace{-4ex}
\end{wrapfigure}

The results of the second experiment, shown in~\cref{fig:exp2-time-vs-reg},
seem to confirm our expectations. Compared to the previous experiment, we observe
that many surrogate families consistently achieved worse regression
performance and prediction times in a more complex, unrestricted domain. The least
affected models appear to be gradient boosted trees, artificial neural networks and extremely
randomised trees, which are known to be capable of capturing relationships
involving mixed feature types that were deliberately withheld in the first
experiment. With only negligible differences, the first two of these families
appear to be tied for the best performance as well as the shortest prediction
time. While extremely randomised trees and radial basis functions also
demonstrated satisfactory properties, other families failed to achieve
comparable regression performance, and in some cases also prediction time.
